\documentclass[line, margin]{res}
%\usepackage[tmargin=2cm]{geometry}
\usepackage{tabularx}

% \newcolumntype{body}{p{\dimexpr \linewidth-3cm \relax}}
% \newcolumntype{date}{p{3cm}}

\begin{document}
\name{Anastasios A. Manganaris}
\address{manganaris.2@buckeyemail.osu.edu \\ 8590 St. Ives Pl., Cincinnati, Ohio 45255 \\ (513) 432-1399}

% Help: https://www.maxburstein.com/blog/creating-resume-using-latex/

\begin{resume}

  \section{EDUCATION}

  \textbf{The Ohio State University}, Columbus, Ohio \hfill May 2023 \\
  Computer Science and Engineering B.S., Specializing in A.I. \hfill GPA: 3.904 \\
  \begin{tabular}{m{0.8in} p{4in}}
    Courses: & Calculus, Linear Algebra, Differential
    Equations, Algorithms and Data Structures, Computer Systems, Web
    Application Development, Techniques in A.I., Computer
    Architecture, Neural Networks, Machine Learning Theory,
    Programming Languages, Database Systems, Parallel Computing,
    Computer Vision, Automata \& Formal Languages, Compiler Design and
    Implementation, Realtime Rendering \\
  \end{tabular}

  \textbf{Anderson High School}, Cincinnati, Ohio \hfill June 2019 \\
  Graduated with Honors, Ranked 13th out of 300 \hfill GPA: 4.663 \\

  \section{EXPERIENCE}

  \textbf{Research Assistant at The Ohio State University} \hfill December 2021 - Present \\
  Helped develop and explore software for identifying RNA chemical
  modifications from Nanopore sequencing data. Helped co-author a manuscript by
  producing findings, figures, and tools for Dr. Sanggu Kim and his
  lab. Investigated relationship between Nanopore sequence quality and
  RNA secondary and tertiary structures.

  \textbf{Software Developer at SentriLock, LLC} \hfill June 2018 - August 2018 \\
  Made a web application for SentriLock's analytics dashboard, which visualized
  lock-box accesses with a heat map overlayed on an interactive map. \\

  \section{PROJECTS}

  \begin{tabularx}{\linewidth}{ @{}X  p{1in} }
    \textbf{multi-cam tool} - An Android App (written in Kotlin) for
    stereo photography. & November 2022 \\
    \\
    \textbf{sclip} - A C program for retroactively capturing audio using the
    JACK sound server API.  & April 2021 \\
    \\
    \textbf{graphdoc} - A Haskell program for converting graphs of markup files
    while preserving their structure.  & September 2020 \\
  \end{tabularx}

  \section{SKILLS}

  \begin{tabularx}{\linewidth}{ @{}X }
    \textbf{Programming Languages}: Haskell, Common Lisp, GNU Guile, Java, C,
    C++, Rust, Python, MATLAB, Ruby, JavaScript, PHP \\
    \textbf{Software \& Services}: Linux, Docker, AWS, Slurm,
    OpenMP, MPI, Emacs, Git, Rails, ReactJS, Nix, and GNU Guix. \\
  \end{tabularx}

  \section{HONORS \& ACTIVITIES}

  \begin{tabularx}{\linewidth}{ @{}X  p{1in} }
    Project Leader for OSU's Code4Community Club &                     2021 - Present \\
    BuckeyeCTF OSU Division 2\textsuperscript{nd} Place &              October 2022 \\
    Buckeye Programming Competition OSU 6\textsuperscript{th} Place &  October 2022 \\
    BuckeyeCTF OSU Division 1\textsuperscript{st} Place &              October 2021 \\
    OSU Maximus Scholarship &                                          May 2019 \\
    IBM James Watson Memorial Scholarship &                            May 2019 \\
    %% Doris Outstanding Senior in Mathematics Award &                    April 2019 \\
    Ohio State Champions with the 7$\sigma$ FTC Robotics Team &        January 2019 \\
    Induction to the Cum Laude Society &                               October 2018 \\
    Induction to the National Honor Society &                          March 2018 \\
    Lead Programmer for 7$\sigma$ FTC Robotics Team  &                 2017 - 2019 \\
  \end{tabularx}

\end{resume}
\end{document}
